--- 
title: "Singapore Society in Numbers"
author: "Shannon Ang"
date: "Last updated: `r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
classoption: openany
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Understanding Singapore through quantitative social science"
---

```{r eval=FALSE, echo=FALSE}
bookdown::render_book("index.Rmd", "all")
```

# Preface {-}
This online book is a compilation of resources to advance quantitative social science in Singapore. It is in progress, and as far as possible, will constantly be updated. The main goal is to promote interest and rigour in quantitative social science on Singapore. It does so by: 

1. Providing information on *Singapore-relevant datasets* that are currently used to answer research and policy questions. This includes: 
  + Descriptions of _publicly available_ datasets and how to access them. This overview of the 'data landscape' will be helpful for social scientists to get started with research on Singapore, and prevent wasteful overlap in primary data collection across institutions.
  + A list of _non-publicly available_ or _restricted_ datasets that could be used to answer important research or policy questions if access was granted. If available, details on the dataset and reasons for data restriction will also be listed. It is hoped that this list will promote greater transparency in data sharing across research teams.
  
2. Maintaining a repository of _replicable_ case studies (with annotated code, where possible) on Singapore society which can be used for illustrations in any quantitatively oriented college-level class. These may be short summaries (blog-length) of published work, or side analyses that may not be appropriate for an academic journal but are useful for Singapore social science nonetheless.

3. Occasional think pieces by researchers on best practices and on how to improve quantitative social science in Singapore.

## About me

## Why I set this up

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


